Sperm do not evolve to collaborate in female meiotic drive.

### 2014-05-07 writeup_and_notes/male_dependent_drive.tex
fixed bug in iterate_drive_model.R

The positive frequency dependence of a self-promoting driver can
induce bistability in its spread, i.e. there is a critical frequency
above which it can spread and below which it moves towards loss. 
Compared to the invasion criteria, the bistable parameter space allowing fixations is much broader -- 
	a common, recessive, self-promoting driver fixes if
        $s<(2d-1)/2$ approximately. 
Therefore, when $(2 d - 1)/(4 d)<s<(2d-1)/(2)$, 
	a recessive, self-promoting driver will deterministically fix if drift, mutation, 
	or migration pressure bring its frequency above $(1-2d+4ds)/(2s(2d-1))$, 
	but it will be lost otherwise.
Inclusion of a heterozygous fitness cost (i.e. $w_{AB}=1-h_s$)
	further constrains the evolution of a self-promoting driver. 
This case also displays bistability -- with any heterozygous fitness cost, a rare self-promoting driver cannot spread. 
However, if $s < d - 1/2+s_h(3-2d)/2$, 
	it will fix deterministically if its 
	frequency is greater than a threshold, $f_B^*$ [Equation \eqref{thresh2}, and \yb{FIGURES SXX}].
%	because it pays the  heterozygous fitness cost but drives
 %      ineffectively (see Figure S\ref{bistable_additive})
%While a standard female driver invades from low frequency when the transmission advantage outweighs the fitness cost (XXX),
%	a rare self-promoter pays a fitness cost, but drives only weakly because complementary sperm are uncommon. 
%This frequency-independent fitness cost, and positive frequency dependent drive generates a bistable system. 
%Below a cutoff frequency the self-promoter driver deterministically decreases in frequency 
%	because it pays the  heterozygous fitness cost but drives
 %      ineffectively (see Figure S\ref{bistable_additive}). 
%Above this frequency, the allele increases deterministically because the commonness of complementary sperm 
%	make drive effective enough to overcome the associated fitness cost.
This bistability prevents self-promoting drivers from invading 	
	reasonably sized populations, and assures that, if they do invade, they will rapidly fix.
Our model therefore predicts that self-promoting drivers will not be
observed as stable polymorphisms in natural populations.

>>>>

The positive frequency dependence of a self-promoting driver can
induce bistability in its spread, i.e. there is a critical frequency
above which it can spread and below which it moves towards loss. 
Compared to the invasion criteria, the parameter space
allowing the fixation of the allele if it is above a cutoff frequency is much broader -- 
	a common, recessive, self-promoting driver fixes if
        $s<(2d-1)/2$ approximately. 
Therefore, when $(2 d - 1)/(4 d)<s<(2d-1)/(2)$, 
	a recessive, self-promoting driver will deterministically fix if drift, mutation, 
	or migration pressure bring its frequency above $(1-2d+4ds)/(2s(2d-1))$, 
	but it will be lost otherwise.
Inclusion of a heterozygous fitness cost (i.e. $w_{AB}=1-h_s$)
	further constrains the evolution of a self-promoting driver. 
This case also displays bistability -- with any heterozygous fitness cost, a rare self-promoting driver cannot spread. 
However, if $s < d - 1/2+s_h(3-2d)/2$, 
	it will fix deterministically if its 
	frequency is greater than a threshold, $f_B^*$ [Equation \eqref{thresh2}, and \yb{FIGURES SXX}].
%	because it pays the  heterozygous fitness cost but drives
 %      ineffectively (see Figure S\ref{bistable_additive})
%While a standard female driver invades from low frequency when the transmission advantage outweighs the fitness cost (XXX),
%	a rare self-promoter pays a fitness cost, but drives only weakly because complementary sperm are uncommon. 
%This frequency-independent fitness cost, and positive frequency dependent drive generates a bistable system. 
%Below a cutoff frequency the self-promoter driver deterministically decreases in frequency 
%	because it pays the  heterozygous fitness cost but drives
 %      ineffectively (see Figure S\ref{bistable_additive}). 
%Above this frequency, the allele increases deterministically because the commonness of complementary sperm 
%	make drive effective enough to overcome the associated fitness cost.
This bistability prevents self-promoting drivers from invading 	
	reasonably sized populations, and assures that, if they do invade, they will rapidly fix.
Our model therefore predicts that self-promoting drivers will not be
observed as stable polymorphisms in natural populations.
